\chapter{Abstract}
\label{ch:abstract}
In 1953, a group of Christian educators and local gentries got together to establish an agricultural and engineering college in Taiwan to train science and engineering talent in the Christian spirit. After several name changes and long preparations, the Chung Yuan Christian College of Science and Engineering (CYCC) was established in October 1955 upon approval by the Ministry of Education. With "education through honest, diligent pursuit and practical experience" as the school`s motto, the College was composed of four departments, namely, the departments of physics, chemistry, chemical engineering, and civil engineering. Upgraded to the status of a full university, CYCC was renamed Chung Yuan Christian University (CYCU) on Aug. 1, 1980. 
\par
After five decades, CYCU has developed with support from all members of the Board of Trustees, as well as immense contributions from past presidents and administrators, Kuo Ke-tee, Hsieh Ming-shan, Han Wei, Yuan Ta-nien, Yin Shiu-hau, Chang Kwang-cheng , Hsiung Shen-kan, and Cheng Wan-lee who represents stages in CYCU creation, foundation, growth, steadfastness, and expansion. The University enrolls students in seven-granting school and colleges, such as the College of Science, Engineering, Business, Design, Electrical Engineering and Computer Science, Humanities and Education, and the School of Law. The university offers 38 graduate programs and 13 Ph.D. programs in 29 departments. There are more than 120,000 alumni and most of them devote their best to the progress of society. 
\par
\clearpage
With a vision for the future, “Integrating,”“Creativity,”“Innovation,” are the competitive advantages of CYCU. By adhering to its educational philosophy and mission, “Holistic Education,” “Human Concern,” and “Service Learning” are the development objectives of CYCU. Furthermore, CYCU has been ranked as the integrated and most prestigious institution of higher education among private universities by Ministry of Education since 1995. Thus, with this responsibility, CYCU devotes to upgrading the level of higher education in Taiwan. Being the leading private university in Taiwan, CYCU intends to raise its reputation in the world; to achieve the goal of being a “faith, hope, and love” integrated university in Taiwan. 

